This is an example of article title

### 2019-05-31 paper/paper.tex
final results, and starting to write experimens

@@

\section{Experiments}
\label{sec:experiments}
%
\begin{figure}[htb]
\centerline{\includegraphics[width=0.99\linewidth]{fig/chipsort-bench-8k.pdf}}
\centerline{\includegraphics[width=0.99\linewidth]{fig/chipsort-bench-256k.pdf}}
\caption{Empirical CDF from {\tt chipsort\_medium!} with 8k {\tt UInt32} values and {\tt chipsort\_large} with 256k values. Results from 10,000 measurements. Speedups are 14\% and 3\%.}
\label{fig:bench-cdf}
\end{figure}

@@

>>>>

Despite the interest due to parallelization, as the experiments show Combsort can display a great performance even in a serial version.

@@

\section{Experiments}
\label{sec:experiments}
%

\subsection{Small arrays}
In our first experiment we evaluate the sorting of small arrays, with only 64 32-bit values. The ChipSort method based on sorting and bitonic merge networks was compared to Insertion sort and the mixed Comb and insertion sort. The small size of the array, and the small running time of the functions make it challenging to perform proper measurements. Our experimental task was therefore to sort 128 sequences of 64 contiguous values in memory, forming a single block of $2^13$ random entries. The in-place sorting functions were applied in sequence, in a for-loop. The results are in Table~\ref{tab:bench-small}.

The {\tt chipsort\_small} function achieved a significant speed-up of over 3 times compared to Insertion sort or the Julia standard function, and twice over Combsort with Insertion sort.

\begin{table}[h]
\tabcolsep22pt
\tbl{Sorting $128 \times 64$ {\tt UInt32} elements.}{
\begin{tabular}{|l|r|}\hline
Method & Median time\\\hline
ChipSort small & 57.206 $\mu$s\\\hline
Comb+Insertion & 133.510 $\mu$s\\\hline
Insertion sort & 194.679 $\mu$s\\\hline
Julia standard & 222.910 $\mu$s\\\hline
\end{tabular}}
\label{tab:bench-small}
\end{table}

The mixed Combsort plus Insertion sort works by proceeding like the regular Combsort until the interval size is unit, and then it switches to insertion sort. This is in a way similar to the Julia standard library, which is Quicksort switching to Insertion sort if the array is too small, with the difference that it is not a divide-and-conquer approach, and therefore in the mixed Combsort the final application of Insertion goes only once, and throught the whole array. This first experiment already demonstrates the potential of this method. Even though the parallelized function was clearly faster, the mixed Combsort also presented a speedup of at least 46\% compared to the other alternatives.

\subsection{Medium and large arrays}
In our second experiment we compared many different methods on inputs of exponentially increasing sizes, from $2^6$ up to $2^{20}$.

@@

\begin{figure}[htb]
\centerline{\includegraphics[width=0.99\linewidth]{fig/chipsort-bench-8k.pdf}}
\centerline{\includegraphics[width=0.99\linewidth]{fig/chipsort-bench-256k.pdf}}
\caption{Empirical CDF from {\tt chipsort\_medium!} with 8k {\tt UInt32} values and {\tt chipsort\_large} with 256k values. Results from 10,000 measurements. Speedups are 7.3\% and 4.4\%.}
\label{fig:bench-cdf}
\end{figure}

\begin{figure}[htb]
\centerline{\includegraphics[width=0.99\linewidth]{fig/chipsort-bench-time.pdf}}
\caption{Running time of the different sorting methods studied.}
\label{fig:bench-cdf}
\end{figure}
